% Updated AltaCV template for Nick Moore - January 2026
% Compiles with pdfLaTeX, XeLaTeX, LuaLaTeX
\documentclass[10pt,a4paper,withhyper]{altacv}
\geometry{left=1.25cm,right=1.25cm,top=1.5cm,bottom=1.5cm,columnsep=1.2cm}

\usepackage{paracol}

\iftutex
  \setmainfont{Roboto Slab}
  \setsansfont{Lato}
  \renewcommand{\familydefault}{\sfdefault}
\else
  \usepackage[rm]{roboto}
  \usepackage[defaultsans]{lato}
  \renewcommand{\familydefault}{\sfdefault}
\fi

% Colors - keeping your suggested palette with subtle tech vibe
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\definecolor{DarkPastelRed}{HTML}{450808}
\definecolor{PastelRed}{HTML}{8F0D0D}
\definecolor{GoldenEarth}{HTML}{E7D192}
\colorlet{name}{black}
\colorlet{tagline}{PastelRed}
\colorlet{heading}{DarkPastelRed}
\colorlet{headingrule}{GoldenEarth}
\colorlet{subheading}{PastelRed}
\colorlet{accent}{PastelRed}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

\renewcommand{\namefont}{\Huge\rmfamily\bfseries}
\renewcommand{\cvsectionfont}{\LARGE\rmfamily\bfseries}
\renewcommand{\cvsubsectionfont}{\large\bfseries}
\renewcommand{\cvItemMarker}{{\small\textbullet}}

\begin{document}

\name{Nick Moore}
\tagline{Principal SRE \& Platform Engineer}

% Optional: add a professional photo if you have one (uncomment & upload image)
% \photoR{2.8cm}{your-photo.jpg}

\personalinfo{%
  \email{nick.moore@pm.me}
  \phone{303-515-1883}
  \location{Littleton / Denver, Colorado, United States}
  \homepage{nick-moore.lovable.app}
  \linkedin{nicholasmoore}
  % \xtwitter{your-handle} % add if you have X/Twitter
  \github{holynakamoto}   % add if public GitHub exists
}

\makecvheader

\columnratio{0.6} % Left column wider for experience

\begin{paracol}{2}

\cvsection{Professional Summary}
AI-savvy Principal SRE \& Platform Engineer with 10+ years designing, scaling, and securing high-traffic infrastructures on AWS, Azure, GCP. CKA-certified expert in Kubernetes (Level 10), Terraform (Level 9), Ansible (Level 10), Docker (Level 10), GitHub Actions (Level 9). Proven in incident response, 99.9\% uptime, cost optimization (20–40\% reductions), and automation at global scale (Pinterest, Talkdesk, financial systems).

Evolving to DevSecOps platform engineering: championing Internal Developer Platforms with Backstage.io + Crossplane for golden paths, shift-left security via Trivy/container/IaC scans, and AI-assisted workflows (Cursor AI, Anthropic Claude, Continue.dev, LangChain) to embed compliance, speed, and soul into self-service development. Always grateful, crafting resilient, meaningful tech that resonates.

\cvsection{Experience}

\cvevent{Principal SRE}{Talkdesk}{Jan 2024 -- Present}{Remote / Denver, CO}
\begin{itemize}
\item Own AWS infrastructure for high-traffic cloud contact center; ensure reliability, scalability, performance.
\item Lead on-call \& incident management; proactive automation to eliminate recurring issues.
\item Kubernetes orchestration, Python routing/orchestration, observability; plan AI feature scaling.
\item Automate provisioning; explore Backstage.io + Crossplane golden paths with embedded security.
\item Integrate shift-left: Trivy scans, AI agents (Cursor/Claude/Continue.dev) for secure code/fixes.
\end{itemize}

\divider

\cvevent{Network Automation Architect}{Pinterest}{Jan 2022 -- Dec 2024}{Remote}
\begin{itemize}
\item Architected AWS network/infra automation for platform serving millions daily.
\item Built Python/Ansible/Terraform pipelines; reduced config time $\sim$60\%, manual toil.
\item Designed high-performance routing/workloads; supported capacity planning, observability.
\item Laid platform engineering foundations, including standardized secure deployments \& IDP concepts.
\end{itemize}

\divider

\cvevent{VP Site Reliability Engineering}{City National Bank}{Jan 2020 -- Jan 2022}{}
\begin{itemize}
\item Led SRE team for critical financial systems (Azure + multi-cloud); ensured compliance, SLAs.
\item Directed incident response, production stability in regulated environment.
\item Scaled via containers, CI/CD, Python monitoring/capacity tools.
\item Advanced automation \& security practices to reduce toil, strengthen posture.
\end{itemize}

\divider

\cvevent{SRE \& Network Automation Consultant}{Independent / Various Clients}{Jun 2018 -- Present}{Remote}
\begin{itemize}
\item Multi-cloud infra (AWS/Azure/GCP) with Terraform/Ansible; 25\% faster deployments, 20\% fewer errors.
\item Kubernetes clusters (Helm), SDN (OpenFlow/VXLAN/libvirt/KVM); 99.9\% uptime.
\item Scaled Edgecast CDN 8GB $\to$ 45TB (95\% cache-hit, WAF/DDoS); 20–40\% latency/cost wins.
\item Built Gemini Prime crypto platform; low-latency, compliant institutional trading.
\item Integrated AI (LangChain/N8N/Zapier/Pipedream), Windsurf UI, Cursor AI for rapid development.
\end{itemize}

\switchcolumn

\cvsection{Skills}
\cvtag{AWS (Expert)}
\cvtag{Terraform (Lv9)}
\cvtag{Ansible (Lv10)}
\cvtag{Kubernetes (CKA, Lv10)}
\cvtag{Docker (Lv10)}
\cvtag{GitHub Actions (Lv9)}
\cvtag{DevSecOps • Shift-Left}
\cvtag{Trivy • Backstage.io}
\cvtag{Crossplane • Golden Paths}
\cvtag{Python • Rust • Golang}
\cvtag{Cursor AI • Claude • LangChain}
\cvtag{N8N • Zapier • Pipedream}
\cvtag{Windsurf UI • SDN/VXLAN}
\cvtag{Observability • Incident Mgmt}
\cvtag{99.9\% Uptime Engineering}

\medskip

\cvsection{Education}
\cvevent{BS Computer Science}{University of Washington}{Sep 1996 -- Jun 2000}{}

\cvsection{Certifications}
\cvachievement{\faCertificate}{Certified Kubernetes Administrator (CKA)}{Cloud Native Computing Foundation}
\cvachievement{\faCertificate}{Terraform (Level 9 Mastery)}{}
\cvachievement{\faCertificate}{Ansible (Level 10 Mastery)}{}
\cvachievement{\faCertificate}{Docker (Level 10 Mastery)}{}
\cvachievement{\faCertificate}{Kubernetes (Level 10 Mastery)}{}
\cvachievement{\faCertificate}{GitHub Actions (Level 9 Mastery)}{}

\cvsection{Highlights}
\cvachievement{\faTrophy}{23 Elite Skills • 23 Legendary}{1.44M+ Total XP • 99.9\% Mastery Rate}
\cvachievement{\faRocket}{Recent Thought Leadership}{Golden Paths \& Crossplane, Backstage IaC Reference Impl, AI SRE Accuracy, Quantum/Agentic Commerce (2025--2026 posts)}

\end{paracol}

\end{document}
